%-------------------------
% Resume in Latex
% Author : Abey George
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


% \pagestyle{fancy}
% \fancyhf{}  % clear all header and footer fields
% \fancyfoot{}
% \renewcommand{\headrulewidth}{0pt}
% \renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Ajajul Ansari} \\ \vspace{1pt}
    Vijay Nagar, Near Balaji Jwellers, Antop Hill, Wadala East, Mumbai, 400037
    \\ \vspace{1pt}
    \small \href{tel:+xxxxxxxxxxxx}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-9082141180} ~} \href{ajajul78692apt@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ajajul78692apt@gmail.com}}
    ~ 
    \href{https://www.linkedin.com/in/ajajul5}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{Linkedin}}
    ~
    \href{https://github.com/ajajul5}{\raisebox{-0.2\height}\faGithub\ \underline{GituHub}} ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KPB HINDUJA COLLAGE}{2016 - 2019}
      {Bachelor in Computer Application (BCA)}{Mumbai, India}
      \vspace{7pt}
  \resumeSubHeadingListEnd



%------RELEVANT COURSEWORK-------
\section{SKILLS}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-2pt, parsep=5pt]
                \item PHP
                \item Codeigniter
                \item Laravel
                \item Slim
                \item CakePHP
                \item OpenCart
                \item MySQL
                \item PosgreSQL
                \item MongoDB
                \item jQuery
                \item JavaScript
                \item Ajax
                \item Axios
                \item Selenium
                \item Scrapping
                \item HTML/CSS
                \item Bootstrap
                \item GIT
                \item Swagger
                \item Docker
                \item Java
                \item JDBC
                \item ExpressJs
                \item NodeJs
                \item ReactJS
                \item WebSocket
                \item OOPS Concept
                \item Web Development
                \item Jira
                \item Bitbucket
                \item Github
                \item Elastic Search
            \end{itemize}
        \end{multicols}
        \vspace{7pt}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {PurpleBridge \href{https://purplebridge.in}{\raisebox{-0.1\height}\faExternalLink } $|$ \large{Client of Neosoft}}
      {Aug 2023 - Present}
      {\underline{PHP Developer} $|$ \large{Laravel, ExpressJs/NodeJs, Websocket, MySQL, Micro-Srvices, ELK}}{Banglore, India}
      \resumeItemListStart
        \resumeItem{\normalsize{Purple Bridge Innovations specializes in custom software development, offering tailored IT services like cloud computing, mobile tech solutions, and user-centric design.}}
        \resumeItem{\normalsize{Techs Platform: The company owns and operates the Ed-tech platform Tap2crack, Finance techs like Rufilo, Tradofina, Plebgraph}}
      \resumeItemListEnd

    \resumeSubheading
      {Vibing Techcloudpro \href{https://techcloudpro.com}{\raisebox{-0.1\height}\faExternalLink }}
      {Mar 2023 - July 2023}
      {\underline{PHP Developer} $|$ \large{OpenCart, MySQL}}{Banglore, India}
      \resumeItemListStart
        \resumeItem{\normalsize{Digital Transformation Experts with core focus on ERP, Cyber Security, RPA, Business Process Automation using AI 4.0}}
      \resumeItemListEnd

      \resumeSubheading
        {Rentokil PCI \href{https://www.rentokil-pestcontrolindia.com}{\raisebox{-0.1\height}\faExternalLink }}
        {Nov 2021 - Mar 2023}
        {\underline{PHP Developer} $|$ \large{PHP, CodeIgniter, MySQL}} {Mumbai, India}
        \resumeItemListStart
          \resumeItem{\normalsize{Rentokil PCI is the Expert in Pest Control, offering effective solutions for more than 100 years globally and over six decades in India. Rentokil is listed on LSE and is a constituent of the FTSE 100 index.}}
        \resumeItemListEnd
        
        \resumeSubheading
          {Atos India \href{https://atos.net}{\raisebox{-0.1\height}\faExternalLink }}
          {Aug 2021 - Oct 2021}
          {\underline{PHP Developer} $|$ \large{CackePHP, PosgreSQL}}{Mumbai, India}
          \resumeItemListStart
            \resumeItem{\normalsize{Atos is a global leader in digital transformation with 111,000 employees and annual revenue of c. €11 billion. European number one in cybersecurity, cloud and high performance computing.}}
          \resumeItemListEnd

        \resumeSubheading
          {Ebrandz LLP \href{https://www.ebrandz.in}{\raisebox{-0.1\height}\faExternalLink }}
          {Jun 2019 - Jun 2021}
          {\underline{PHP Developer} $|$ \large{CodeIgniter, Slim, MySQL, MongoDB}}{Mumbai, India}
          \resumeItemListStart
            \resumeItem{\normalsize{The company has been recognized as 'One of the BEST SEARCH ENGINE OPTIMIZATION Providers in the WORLD' by DIGIT MAGAZINE.}}
          \resumeItemListEnd
        
  \resumeSubHeadingListEnd
\vspace{-12pt}
%-----------PROJECTS-----------
\section{PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
       \resumeProjectHeading
          {{\textbf{\large{Common Integrations for below projects.}}}}{2019 - Present}
          \resumeItemListStart
          \resumeItem{\normalsize{\textbf{Authentication:} Integrated social login via Google, Facebook, GitHub, and JWT token-based authentication.}}
          \resumeItem{\normalsize{\textbf{Mailing:} Configured and optimized mailing systems using SMTP and AWS SES.}}
          \resumeItem{\normalsize{\textbf{Automation:} Developed and managed cron jobs, queue workers, and data scraping processes.}}
          \resumeItem{\normalsize{\textbf{Reporting:} Implemented export functionalities to PDF, Excel, CSV, and Images with automated uploads to Google Drive.}}
          \resumeItem{\normalsize{\textbf{Payment Integration:} Integrated payment gateways, including Bill Desk and Razorpay.}}
          \resumeItem{\normalsize{\textbf{API Development \& Micro-Services::} Designed and deployed RESTful APIs for seamless interaction with project features.}}
          \resumeItemListEnd 
          \vspace{-9pt}

          
      \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Micro Services}}} } $|$ \large{Laravel, MySQL}}{Aug 2023 - Present}
          \resumeItemListStart
            \resumeItem{\normalsize{\textbf{Payment Service}.}}
            \resumeItemListStart
                \resumeItem{\normalsize{Developed and maintained a microservice for handling diverse payment types.}}
                \resumeItem{\normalsize{Integrated with multiple payment partners, including Yes Bank, Razorpay, PayU, Paynimo, Cashfree.}}
                \resumeItem{\normalsize{Supported various payment methods such as Payment Gateway, UPI Intent, E-Collect, and Bank Transfer.}}
                \resumeItem{\normalsize{Managed end-to-end payment processes, including initiation, creation, surcharges, and verification.}}
            \resumeItemListEnd
            \resumeItem{\normalsize{\textbf{Loan Service :} for repayment processes, including types of loans and calculations for repayments and dues.}}
            \resumeItem{\normalsize{\textbf{Third-Party Service :} for verify users' PAN and assess loan amount eligibility based on credit scores.}}
            \resumeItem{\normalsize{\textbf{Event Service :} for communication through web engagement for active loans.}}
            \resumeItem{\normalsize{\textbf{Master Service:} for storing all types of master data, including Bank IFSC and Bank Master.}}
            \resumeItem{\normalsize{\textbf{External Gateway:} for managing webhooks, receiving various types of payment webhooks.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Purple Pharma}}} \href{}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Laravel, MySQL}}{Apr 2024 - Jul 2024}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a comprehensive dashboard for managing doctors, chemists, products, gifts, and users with specific roles and permissions (BO, SBO, ABM, RBM, ZSM, NSM, GM, VP, President, Director, Admin).}}
            \resumeItem{\normalsize{Enabled BOs and SBOs (Medical Representatives) to file Daily Call Reports (DCRs), track doctor and chemist visits, manage campaigns, assign products, handle gifting, track personal expenses, and monitor business outcomes.}}
            \resumeItem{\normalsize{Established a clear hierarchy and approval process between roles, ensuring structured workflow and accountability.}}
            \resumeItem{\normalsize{Implemented a mapping feature for reassigning doctors, chemists, and subordinates when users leave the organization.}}
            \resumeItem{\normalsize{Designed an approval matrix across modules where necessary streamline operations and ensure compliance.}}
            \resumeItem{\normalsize{Enhanced data security by implementing role-based access control, ensuring that users only have access to relevant information and features.}}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Tap2Crack Chat App}}} \href{}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{ExprssJs, NodeJs, Websocket, MySQL}}{Jul 2024 - Present}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a chat application for live class.}}
            \resumeItem{\normalsize{Chat has multiple feartures like create Rooms, 1-1 chatting also has notifications, kicking users form rooms.}}
            \resumeItem{\normalsize{Handling permissions for modarator and simple student.}}
          \resumeItemListEnd
          \vspace{-13pt}

        \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Tap2Crack Admin Gateway}}} \href{}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Laravel, Redis, Cache, MySQL}}{Mar 2024 - May 2024}
          \resumeItemListStart
            \resumeItem{\normalsize{Tap2crack has many features like. Management of roles, categories, subjects, students, exams, courses, books, coupons, study materials, purchases and many more. }}
            \resumeItem{\normalsize{Developed a Test Series feature that allows users to create sections and add questions with assigned marks.}}
            \resumeItem{\normalsize{Implemented a drag-and-drop feature for easy creation of question sets.}}
            \resumeItem{\normalsize{Created a folder hierarchy in the course section to help users easily locate, upload, and modify files and folders.}}
          \resumeItemListEnd
          \vspace{-13pt}
        
      \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Tap2Crack Blog}}} \href{}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Laravel, MySQL}}{Jun 2024 - Jun 2024}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a dashboard enabling users to manage categories, upload prospect images, and write blogs that automatically sync to the Tap2Crack blog site.}}
            \resumeItem{\normalsize{Tap2crack Blogs has 3 screens.}}
            \resumeItemListStart
                \resumeItem{\normalsize{\textbf{Homepage:} Displays each category with the six latest articles.}}
                \resumeItem{\normalsize{\textbf{Category:} Lists all articles associated with a specific category.}}
                \resumeItem{\normalsize{\textbf{Articals:} Provides detailed reading of Articles, displays related articles, and includes course navigation links.}}
            \resumeItemListEnd
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\href{}{\textbf{\large{\underline{Short Url Generator}}} \href{}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Laravel, MySQL}}{Aug 2024 - Aug 2024}
          \resumeItemListStart
            \resumeItem{\normalsize{A URL shortening service that allows users to create shortened links, making long URLs more manageable and trackable.}}
            \resumeItem{\normalsize{This application is mapped for various devices and products, including desktop and Android devices.}}
            \resumeItem{\normalsize{\textbf{The link has three behaviors:} Web Only, App Only, and App then Web Only.}}
            \resumeItem{\normalsize{When the link is triggered by a desktop, it redirects to the full URL.}}
            \resumeItem{\normalsize{When the link is triggered by a mobile device, it attempts to launch the respective app; if the app is not found, it redirects to the Play Store or the full URL in the mobile browser.}}
            \resumeItem{\normalsize{A dashboard is provided for tracking and managing shortened links efficiently.}}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\href{https://partnerportal.ai}{\textbf{\large{\underline{Partner Portal}}} \href{https://partnerportal.ai}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{OpenCart, MySQL}}{Mar 2023 - July 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Cloud-based, AI-powered Vendor Management Platform.}}
            \resumeItem{\normalsize{Developed company and vendor product relationships, enabling companies to order products from vendors and vendors to view their product orders.}}
            \resumeItem{\normalsize{Implemented data synchronization between Celigo, Netsuite, and Partner Portal through custom APIs.}}
            \resumeItem{\normalsize{Designed and built dashboards with comprehensive filter options for data analysis.}}
            \resumeItem{\normalsize{Created dynamic HTML input fields for public form, allowing users to customize and reorder fields as needed.}}
            \resumeItem{\normalsize{Integrated GST validation API for compliance.}}
            \resumeItem{\normalsize{Developed API for document uploads to AWS S3.}}
            \resumeItem{\normalsize{Established webhooks to ensure seamless data synchronization between Partner Portal, Netsuite, and Celigo.}}
            \resumeItem{\normalsize{Managed data access restrictions across Super Admin, company, vendor, and five additional user groups.}}
            \resumeItem{\normalsize{Addressed and resolved daily bugs using Jira.}}
            \resumeItem{\normalsize{Utilized MySQL for efficient data storage and retrieval.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{ODSAPI}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Laravel, MySQL}}{Mar 2023 - July 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed APIs to fetch and store Shopify data (Products, Sales, Orders, Payments) in MongoDB.}}
            \resumeItem{\normalsize{Created APIs for syncing data with Netsuite, tailored for companies and their vendors.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Indent Portal}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed to manage product licenses with full CRUD operations, including alerts for upcoming expirations.}}
            \resumeItem{\normalsize{Implemented an approval matrix for indents based on financial thresholds.}}
            \resumeItem{\normalsize{Set up automated notifications for product license expiration.}}
            \resumeItem{\normalsize{Successfully migrated the project to the Laravel framework.}}
          \resumeItemListEnd
          \vspace{-13pt}
      
      \resumeProjectHeading
          {{\textbf{\large{\underline{TRF (Termination Request Form) Portal}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Built a dashboard to monitor contract statuses among submitters, approvers, and financiers.}}
            \resumeItem{\normalsize{Developed 5 levels approval matrix with option approval, rejection, or clarification, with visibility for CSEs.}}
            \resumeItem{\normalsize{Implemented a group chat feature within the portal for clarification discussions.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Credit Notes Portal}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a system for updating debtor lists and enabling CSEs to raise credit notes against balance payments.}}
            \resumeItem{\normalsize{Implemented functionality to read and store data from Excel files for processing balance payments.}}
            \resumeItem{\normalsize{Established an approval matrix for credit notes, allowing approvers to accept, reject, or request clarification, with status tracking visible to CSEs.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{PayEasy}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Integrated Razorpay and Bill Desk payment gateways.}}
            \resumeItem{\normalsize{Developed functionality for generating payment links and barcodes for deferred payments.}}
            \resumeItem{\normalsize{Automated confirmation emails to customers, employees, and managers upon successful payment.}}
            \resumeItem{\normalsize{Set up webhooks for real-time payment confirmation.}}
            \resumeItem{\normalsize{Successfully migrated the project to the Laravel framework.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Lead Tracker}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Managed lead submissions and developed dashboards for comprehensive reporting.}}
            \resumeItem{\normalsize{Automated document uploads to Google Drive and enabled lead report exports to Excel and CSV formats, with automatic uploads to Google Drive.}}
            \resumeItem{\normalsize{Developed an API feature to rate leads based on points.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Myclaim}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed a portal for settling employee expense claims, including document upload functionality.}}
            \resumeItem{\normalsize{Implemented a multi-level approval process based on the reporting manager.}}
            \resumeItem{\normalsize{Provided approvers with options to accept or reject claims, along with the ability to add comments.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Daily Sales Performance (DSP)}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{PHP, MySQL}}{Nov 2021 - Mar 2023}
          \resumeItemListStart
            \resumeItem{\normalsize{Designed and enhanced four applications (NKA, SSD, HYG, PSD) to optimize input collection from field agents, streamlining business processes.}}
            \resumeItem{\normalsize{Integrated Google authentication for secure and convenient login, along with JWT for token-based authentication.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {\href{https://ioclanalytics.net/wsp}{\textbf{\large{\underline{Indian Oil Analytics}}}\href{https://ioclanalytics.net/wsp}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{CakePHP, MySQL}}{Aug 2021 - Oct 2021}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed frontend and backend services using CakePHP, with PostgreSQL as the database.}}
            \resumeItem{\normalsize{Implemented reporting features for various time frames (daily, weekly, monthly, etc.).}}
            \resumeItem{\normalsize{Added export functionality for reports into CSV and Excel formats.}}
            \resumeItem{\normalsize{Automated the distribution of daily reports to managers at the area, city, state, and country levels.}}
          \resumeItemListEnd
          \vspace{-13pt}


      \resumeProjectHeading
          {\href{Version7.edeveloperz.com}{\textbf{\large{\underline{Version7.edeveloperz.com}}}\href{Version7.edeveloperz.com}{\raisebox{-0.1\height}\faExternalLink }} $|$ \large{CodeIgniter, MySQL, MongoDB}}{Aug 2021 - Oct 2021}
          \resumeItemListStart
            \resumeItem{\normalsize{Build custom templates daily reports mailing.}}
            \resumeItem{\normalsize{Build PPC reports page with dashboards and custom layouts. With multiple charts and export feature.}}
            \resumeItem{\normalsize{Integrate Woo foo, Google form, Jot form third party API to version7 and version8 dashboard.}}
            \resumeItem{\normalsize{Used Webhooks to monitor events at form submissions.}}
            \resumeItem{\normalsize{Data scraping for generating reports like ratings, reviews of posted business on websites.}}
            \resumeItem{\normalsize{Used Cron jobs to pull data daily from third party data to our database.}}
            \resumeItem{\normalsize{Used CodeIgniter framework for frontend and backend services and MongoDB, MySQL to fetch and store data.}}
          \resumeItemListEnd
          \vspace{-13pt}

      \resumeProjectHeading
          {{\textbf{\large{\underline{Service.edeveloperz.com}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Slim, MySQL, MongoDB}}{Jun 2019 - Jun 2021}
          \resumeItemListStart
            \resumeItem{\normalsize{Developed APIs for Version7 features to facilitate interaction with various front-end platforms and devices.}}
            \resumeItem{\normalsize{Utilized the Slim PHP framework for API development, with Version7 being built in CodeIgniter.}}
          \resumeItemListEnd
          \vspace{-13pt}


      \resumeProjectHeading
          {{\textbf{\large{\underline{Personal Projects}}} {\raisebox{-0.1\height}\faExternalLink }} $|$ \large{Slim, MySQL, MongoDB}}{Jan 2019 - Jan 2022}
          \resumeItemListStart
            \resumeItem{\normalsize{\textbf{Ad Platform:} Developed a Laravel-based platform for buying and selling ads between clients and customers, with MySQL for data management.}}
            \resumeItem{\normalsize{\textbf{Computer Class Management:} Created a system for managing student registration, courses, fees, and certifications using CakePHP and MySQL.}}
            \resumeItem{\normalsize{\textbf{MLM System:} Built a user registration and management system with revenue dashboards for each hierarchical user, using Laravel.}}
            \resumeItem{\normalsize{\textbf{E-commerce Application:} Developed an online gift business platform (cakes, candies, flowers) using Laravel.}}
          \resumeItemListEnd
          \vspace{-13pt}

          
    \resumeSubHeadingListEnd
\vspace{-5pt}
 %-----------CERTIFICATIONS---------------
\section{CERTIFICATIONS}
\begin{itemize}[label=$\bullet$, noitemsep]
    \item Web Designing And PHP Development (ASTERIXSOLUTION). \hfill \textit{Issued: Jan 2019}
    \item Big Data Hadoop Development (ASTERIXSOLUTION). \hfill \textit{Issued: Jan 2018}
    \item Core Java And Advanced Java Development (ASTERIXSOLUTION). \hfill \textit{Issued: Jan 2017}
    \item Diploma on Computer Application, Software Development and Hardware (IT-INFOTECH). \hfill \textit{Issued: Jan 2016}
\end{itemize}
 
%
%-----------PROGRAMMING SKILLS-----------
\section{Personal Information}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Languages:}}{ \normalsize{English, Hindi, Urdu}} \\
     \textbf{\normalsize{Hobbies:}}{ \normalsize{Online Games, Listening Musics, Watching Movies}} \\
     \textbf{\normalsize{Date of birth:}}{\normalsize{ 05 June 1996 }} \\
     \textbf{\normalsize{Nationality:}}{\normalsize{ Indian }} \\
     \textbf{\normalsize{Marital status:}}{\normalsize{ Single }} \\
    }}
 \end{itemize}
 \vspace{-15pt}

\end{document}
